Local Type Inference for Polarised System F with Existentials

### 2023-11-14 oopsla24/tex/04-algorithm.tex
wip: correctness

\subsection{Algorithmic Syntax}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Subtyping Algorithm}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Unification}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Constraint Merge}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Type Upgrade and the Least Upper Bounds}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Anti-Unification}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Type Inference}

@@

This way, the inference algorithm also consists of three mutually recursive procedures: 
the positive type inference, the negative type inference, and the
application type inference.

>>>>

\subsection{Algorithmic Syntax}
\label{sec:algo-syntax}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Subtyping Algorithm}
\label{sec:subtyping-algorithm}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Unification}
\label{sec:unification}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Constraint Merge}
\label{sec:constraint-merge}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Type Upgrade and the Least Upper Bounds}
\label{sec:lub}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Anti-Unification}
\label{sec:antiunification}

@@

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\subsection{Type Inference}
\label{sec:typing}

@@

This way, the inference algorithm also consists of three mutually recursive procedures: 
the positive type inference, the negative type inference, and the
application type inference. As subroutines, the inference algorithm uses
subtyping, constraint merge, and normalization.  
The corresponding graph is shown in \cref{fig:alg-typing-graph}.

\begin{figure}[h]
  \centering
  \begin{tikzpicture}
    [>={Stealth[scale=2]},node distance=2.2cm,every node/.style={draw,rectangle},every text node part/.style={align=center}]
    % Define nodes
    \node[] (1) {Positive Inference\\$[[Γ; Φ ⊨ v : iP]]$};
    \node[right=1.4cm of 1] (2) {Negative Inference\\$[[Γ; Φ ⊨ c : iN]]$};
    \node[right=1.4cm of 2] (3) {Application Inference\\$[[Γ ; Φ ; Θ1 ⊨ uN ● args ⇒> uM ⫤ Θ2 ; SC]]$};
    \node[below of=2,xshift=+2cm] (4) {Constraint Merge\\$[[Θ ⊢ SC1 & SC2 = SC3]]$\\(\cref{sec:constraint-merge})};
    \node[below of=4] (5) {Positive Subtyping\\$[[Γ ; Θ ⊨ uP1 ≥ iP2 ⫤ SC]]$\\(\cref{sec:subtyping-algorithm})};
    \node[left=0.75cm of 4] (6) {Negative Subtyping\\$[[Γ ; Θ ⊨ uN1 ≤ iN2 ⫤ SC]]$\\(\cref{sec:subtyping-algorithm})};
    \draw[->] ([yshift=-.2cm]2.west) to ([yshift=-.2cm]1.east);
    \draw[->] ([yshift=+.2cm]1.east) to ([yshift=+.2cm]2.west);
    \draw[->, bend right=20] (3) to (1);
    \draw[->] (2) to (3);
    \draw[->] (2) to (4);
    \draw[->] (3) to (4);
    \draw[->, bend right] (1.south west) to (5);
    \draw[->, bend left] (3) to (5);
    \draw[->] (2) to (6);
  \end{tikzpicture}  
  \caption{Dependency graph of the typing algorithm}
  \label{fig:alg-typing-graph}
\end{figure}
